Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-19 demystify.tex
Updates from Overleaf

\noindent and its \LaTeX{} source is also on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{Github}. If you have questions or comments, feel free to create new \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issues} or \href{https://github.com/nguyenthanhvuh/phd-cs-us/discussions}{discussions}.

@@

\begin{commentbox}[Vu:]
  One of the reasons I created this document is that my colleagues at GMU are interested in recruiting Vietnamese students and are surprised when seeing very few applications in Vietnam (see \autoref{sec:ack}). Each year our CS PhD program receives about 400 PhD applications, most of which are international but only 4--5 are from Vietnam. In general the number of CS PhD applications from Vietnam to US universities is very low and more would be welcome.
\end{commentbox}

@@

The document might also not sufficient for students aiming for top-10 schools, which might have different requirements\footnote{e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU}.  However, the information here should be useful for students aiming for other good schools, e.g., R1 institutions in the US. It is definitely useful for students aiming for GMU :)

>>>>

\noindent and its \LaTeX{} source is also on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{GitHub}. If you have questions or comments, feel free to create new \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issues} or \href{https://github.com/nguyenthanhvuh/phd-cs-us/discussions}{discussions}.

@@

\begin{commentbox}[Vu:]
  One of the reasons I created this document is that my colleagues at GMU are interested in recruiting Vietnamese students and are surprised when seeing very few applications in Vietnam (see \autoref{sec:ack}). Each year our CS PhD program receives 500+ PhD applications, most of which are international but only 5--6 are from Vietnam. In general the number of CS PhD applications from Vietnam to US universities is very low and more would be welcome.
\end{commentbox}

@@

The document might not be sufficient for students aiming for top-10 schools, which typically have different requirements\footnote{e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU}.  However, the information here should be useful for students aiming for other good schools, e.g., R1 institutions in the US. It is definitely useful for students aiming for GMU :)
